Convex Surrogates via Polyhedral Losses

### 2019-01-31 cvx-fin.tex
continuing in defs

A \emph{property} formally captures the relationship between distributions $p$ and minimizers of expected loss.
In this paper, we will use double arrow notation to mean a mapping to all nonempty subsets.
So the notation $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^{\R} \setminus \emptyset$.

\begin{definition}

\end{definition}

\subsection{Properties and Losses}
\begin{definition}
  A property $\Gamma:\simplex\toto\R$ is a nonempty, set-valued function mapping a probability distribution to the correct report values for the given distribution.

  A \emph{level set} $\Gamma_r := \{p : r \in \Gamma(p)\}$ is the set of distributions $p$ for which the report $r$ is ``optimal''.

\raf{Should bake non-degenerate into the definition: insist that $\Gamma(p) \neq \emptyset$ for all $p$.}

  \raf{I think to avoid a TON of extra mentions of ``non-redundant'' we should take finite to mean finite and non-redundant}
  We call $\Gamma$ a \emph{finite} property is $\R$ is finite, and \emph{nonredundant} if, for all $r$, there is no $u$ so that the level set $\Gamma_r \subseteq \Gamma_u$.
  For simplicity, when we say a property is finite, we also take it to be nonredundant.
\end{definition}

\begin{definition}
  \raf{I realized that (a) it is common to restrict losses to be non-negative, and (b) it solves some annoying issues where we have to say ``if $L$ is bounded below...'' nicely.  So unless any objections, let's say $L \geq 0$.}

  A loss $L:\R\to\reals^\Y_+$, elicits a property $\Gamma:\simplex \toto \R$ if, for all $p \in \simplex$ and $r \in \Gamma(p)$, we observe
  \begin{equation}
  \Gamma(p) = \argmin_{r \in \R} \E_{Y\sim p}[L(r,Y)]
  \end{equation}
  \jessie{Do we want regular elicitation vs essentially elicits...}
\end{definition}

\begin{definition}
  Polyhedral function, loss
\end{definition}

\subsection{Link Functions}

\begin{definition}
  Let properties $\gamma:\simplex\toto\R$ and $\Gamma:\simplex\toto\R'$ be given.
  A \emph{link function} is a map $\psi:\R'\to\R$.
  We say that a link $\psi$ is:
  \begin{itemize}
  \item \emph{Calibrated} if for all $p\in\simplex$, $r'\in \Gamma(p) \implies \psi(r') \in \gamma(p)$; in other words, if for all $r'\in\R'$, $\Gamma_{r'} \subseteq \gamma_{\psi(r')}$;
  \item \emph{Separated}, with respect to a loss $L$ eliciting $\Gamma$, if for all $p \in \simplex$,
  \begin{align*}
  \inf_{u \in \R'; \psi(u) \not \in \gamma(p)} \E_{Y\sim p}[L(u, Y)] > \inf_{u \in \R'}\E_{Y\sim p}[L(u, Y)]~.
  \end{align*}
  \item \emph{Exhaustive} if for all $p\in\simplex$, $\gamma(p) = \psi(\Gamma(p)) := \{\psi(r') : r'\in\Gamma(p)\}$.
  \end{itemize}
\end{definition}

@@

\subsection{Elicitation Complexity}

>>>>

A \emph{property} formally captures the relationship between distributions $p$ and ``optimal'' reports, i.e. those minimizing expected loss.
In this paper, we will use double arrow notation to mean a mapping to all nonempty subsets.
So the notation $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^{\R} \setminus \emptyset$.

\begin{definition}[Property, level set]
  A \emph{property} is a function $\gamma:\simplex\toto\R$ mapping each distribution $p$ to a nonempty subsets of ``correct'' reports.
  A \emph{level set} $\gamma_r := \{p : r \in \gamma(p)\}$ is the set of distributions $p$ for which the report $r$ is correct.
\end{definition}
For example, the \emph{mode} on $n$ outcomes has $\gamma(p) = \{ y : p_y = \max_{y'} p_{y'}\}$.
It is a finite property:

\begin{definition}[Finite property, nonredundant]
  We call $\gamma$ a \emph{finite} property is $\R$ is a finite set and call it \emph{nonredundant} if no level set is a superset of another.
  For simplicity, when we say a property is finite, we also require it to be nonredundant.
\end{definition}

\begin{definition}[Elicits]
  A loss $\ell:\R\to\reals^\Y_+$, \emph{elicits} a property $\gamma:\simplex \toto \R$ if for all $p \in \simplex$,
  \begin{equation}
  \Gamma(p) = \argmin_{r \in \R} \E_{Y\sim p}[L(r,Y)].
  \end{equation}
  \jessie{Do we want regular elicitation vs essentially elicits...}
\end{definition}
For example, one can verify that $0-1$ loss elicits the mode.
The terminology comes from the information elicitation literature, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$; she tries to minimize expected loss.

Typically in this paper, $\gamma$, $\R$, and $\ell$ will be used for a finite property, finite report space, and loss eliciting it, while $\Gamma$, $\R'$ and $L$ will be used for some other property, often with report space $\R' = \reals^d$.
In this case, we prefer $r$ for a member of $\R$ and $u$ for members of $\reals^d$.

In $\reals^d$, a \emph{polyhedral set} is the intersection of a finite number of halfspaces.
A \emph{polytope} is a bounded polyhedral set.
\begin{definition}[Polyhedral loss]
  A \emph{polyhedral function} is a pointwise maximum over a finite set of affine functions.
  In other words, it is a function whose epigraph (set of points lying above it) forms a polyhedral set.
  $L: \reals^d \to \reals^{\Y}_+$ is a \emph{polyhedral loss} if $L(u)_y$ is a polyhedral function of $u$ for each $y$.
\end{definition}

\subsection{Link Functions and Elicitation Complexity}
Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
We now formalize this procedure.
\bo{Maybe mention that previous formalizations are for single-valued properties only if true? And if so, that they don't really apply to finite properties??}

\bo{Didn't touch these}
\begin{definition}
  Let properties $\gamma:\simplex\toto\R$ and $\Gamma:\simplex\toto\R'$ be given.
  A \emph{link function} is a map $\psi:\R'\to\R$.
  We say that a link $\psi$ is:
  \begin{itemize}
  \item \emph{Calibrated} if for all $p\in\simplex$, $r'\in \Gamma(p) \implies \psi(r') \in \gamma(p)$; in other words, if for all $r'\in\R'$, $\Gamma_{r'} \subseteq \gamma_{\psi(r')}$;
  \item \emph{Separated}, with respect to a loss $L$ eliciting $\Gamma$, if for all $p \in \simplex$,
  \begin{align*}
  \inf_{u \in \R'; \psi(u) \not \in \gamma(p)} \E_{Y\sim p}[L(u, Y)] > \inf_{u \in \R'}\E_{Y\sim p}[L(u, Y)]~.
  \end{align*}
  \item \emph{Exhaustive} if for all $p\in\simplex$, $\gamma(p) = \psi(\Gamma(p)) := \{\psi(r') : r'\in\Gamma(p)\}$.
  \end{itemize}
\end{definition}

@@
